
    \medskip

    \myheader{Grants and Funding}

    \medskip
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.1\textwidth}  p{0.8\textwidth}}
     Sep.  2025 --  Aug.  2030 & \textbf{Dynamics of geometrically finite group actions: beyond Kleinian groups}. \textit{Simons Foundation Travel Support for Mathematicians}. (\$37,100)
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] PI(s): H. Bray.
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
 Sep.  2024 & \textbf{4-VA Collaborative Research Grant Award}. \textit{University of Virginia}. (\$30,000)
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] PI(s): J.D. Quigley. Co-PI(s): H. Bray, R. Field, A. Lukyanenko, and A. Moore.
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
 Sep.  2024 & \textbf{4-VA Collaborative Research Matching Grant Award}. \textit{George Mason University}. (\$5,000)
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] PI(s): H. Bray. Co-PI(s): A. Lukyanenko.
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
   2018 --    2022 & \textbf{AMS Simons Research Travel Grant}. \textit{American Mathematical Society}. (\$4,000) \\ 
 Jun.  2019 & \textbf{LG\&TBQ: a conference celebrating LGBTQ+ mathematicians in geometry, topology, and dynamical systems}. \textit{National Science Foundation}. (\$40,000)
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] Co-PI(s): H. Bray and A. Kent.
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
 Jun.  2019 & \textbf{University of Michigan College of Literature, Science, and the Arts Mini-Grant}. \textit{University of Michigan College of Literature, Science, and the Arts}. (\$2,500) \\ 
 Aug.  2016 & \textbf{GEAR Graduate Intern Travel Grant}. \textit{Geometric Structures and Representation Varieties (GEAR) Network}. (\$3,100) \\ 
 Jan.  2016 & \textbf{AMS Graduate Student Travel Grant}. \textit{American Science Foundation}.  \\ 
   2012 --    2014 & \textbf{Tufts GSAS Conference Travel Grant}. \textit{Tufts University Graduate School of Arts and Sciences}.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    

        \bigskip

See Appendix for a list of additional proposals submitted to the NSF and
Simons Foundation.

    
    \medskip

    \myheader{Awards and Honors}

    \medskip
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.1\textwidth}  p{0.8\textwidth}}
     Apr.  2019 & \textbf{The Frederick Gehring Award for Postdoctoral Excellence}. \textit{The University of Michigan Mathematics Department}.  \\ 
 Apr.  2016 & \textbf{Outstanding Academic Scholarship Nominee}. \textit{Tufts University Graduate School of Arts and Sciences}. (Finalist) \\ 
 May  --  Dec.  2015 & \textbf{Graduate Institute for Teaching Fellowship}. \textit{Tufts University Graduate School of Arts and Sciences}.  \\ 
 Oct.  2015 & \textbf{Distinguished Teaching Prize}. \textit{Tufts University Department of Mathematics}.  \\ 
 Apr.  2015 & \textbf{The Robert P. Guertin Graduate Student Leadership Award}. \textit{Tufts University Graduate School of Arts and Sciences}.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    