
    \medskip

    \myheader{Mentoring and Advising}

    \medskip
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
      Fall 2022 --   Spring 2023 & \textbf{Director}. \textit{Mason Experimental Geometry Lab}. 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] Supervised a management team of 6 graduate students and oversaw outreach operations led by a doctoral student and a team of 2 undergraduates and 1 MS student.
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
  Spring 2023 & \textbf{Mason Experimental Geometry Lab (MEGL) Project Mentor}. \textit{Hyperbolic Crochet}.  Nguphuong Au, Merold Saffa, Aidan Self, Sydney Thu (undergraduates, George Mason University). 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] 
            Co-Mentors: Madeline Horton (graduate student, George Mason University) 
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
  Fall 2020 --   Fall 2022 & \textbf{Supervisor}. \textit{George Mason Learning Assistant Program}. 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] Mentored 11 different undergraduate learning assistants (LAs) in my active learning courses over five semesters, with some LAs working with me for up to three semesters. On average, I supervised 14/5=2.8 LAs per semester.
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
  Fall 2020 --   Spring 2022 & \textbf{Director of Outreach}. \textit{Mason Experimental Geometry Lab}. 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] Supervised 4 undergraduates and 2 graduate interns in outreach design and facilitation, including extensive training.
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
  Summer 2020 & \textbf{Advisor}. \textit{University of Michigan Mathematics Department first year honors advising}.  \\ 
  Winter 2020 & \textbf{Lab of Geometry at Michigan (LoGM) Project Mentor}. \textit{Entropy degeneration of ideal projective pants}.  Marianne DeBrito, Andrew Nguyen, Marisa O'Gara (undergraduates, University of Michigan). 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] Preprint authored by DeBrito, Nguyen, and O'Gara submitted for publication.
            Co-Mentors: Giuseppe Martone (postdoc, University of Michigan) and Mitul Islam (graduate student, University of Michigan) 
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
  Fall 2019 & \textbf{Lab of Geometry at Michigan (LoGM) Project Mentor}. \textit{Growth rates of tent maps}.  Robert Buckley, Grace O'Brien, Zoe Zhou (undergraduates, University of Michigan). 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] Preprint authored by Buckley, Chen, O'Brien, and Zhou submitted for publication. Data published in DeepBlue Data.
            Co-Mentors: Samuel Hansen (mathematics and statistics librarian, University of Michigan) 
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
  Fall 2018 & \textbf{Lab of Geometry at Michigan (LoGM) Project Mentor}. \textit{3d printing nonstrictly convex projective structures}.  Steven Schaefer, Rudra Ranganathan, Hanissa Shamsuddin (undergraduates, University of Michigan). 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] 
            Co-Mentors: Samantha Pinella and Robert Walker (graduate students, University of Michigan) 
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
  Summer 2017 & \textbf{Michigan Summer REU  Project Mentor}. \textit{Random walks on the fundamental group of the once punctured torus}.  Jennifer Jones-Baro (undergraduate, Centro de Investigacion en Matem\'aticas) and Adam Holeman (masters student, University of Montana). 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] 
            Co-Mentors: Caleb Ashley (postdoc, University of Michigan) 
        \end{itemize}
        }
        \vspace{-1em}
         
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    