
    \medskip

    \myheader{Pedagogical Training}

    \medskip
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.2}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
      Spring 2021 --   Spring 2022 & \textbf{Teaching Seminar}. \textit{George Mason University}.  Department of Mathematical Sciences. Fairfax, VA.  \\ 
  Winter 2018 --   Winter 2020 & \textbf{Learning Community on Inclusive Teaching (LCIT)}. \textit{University of Michigan}.  Department of Mathematics. Ann Arbor, MI.  \\ 
  Fall 2016 --   Spring 2020 & \textbf{Inquiry Based Learning (IBL) working seminar}. \textit{University of Michigan}.  Department of Mathematics. Ann Arbor, MI.  \\ 
  Summer 2016,   Summer 2017 & \textbf{Inquiry Based Learning (IBL) Workshop}. \textit{University of Michigan}.  Department of Mathematics. Ann Arbor, MI. 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] The annual three day IBL workshop consists of observing and analyzing an inquiry-based learning (IBL) classroom and discussing IBL-style instructional practices.
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
  Summer 2016 & \textbf{Michigan Teaching Training}. \textit{University of Michigan}.  Department of Mathematics. Ann Arbor, MI. 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] The University of Michigan has an extensive teacher training program for new hires, run by the mathematics department in conjunction with the Michigan Center for Research on Learning and Teaching (CRLT).
        \end{itemize}
        }
        \vspace{-1em}
         \\ 
 Spring --   Fall 2016 & \textbf{Graduate Institute for Teaching (GIFT)}. \textit{Tufts University}.  Graduate School of Arts and Sciences. Medford, MA. 
        \hspace{-1em}

        {\small
        \begin{itemize}
        \setlength{\parindent}{0em}
        \item[] The Tufts Graduate Student Institute for Teaching (GIFT) awards fellowships on a competitive basis across all fields of scholarship at Tufts. Teaching fellows participate in an intensive summer workshop
on pedagogy before working with a faculty mentor in the classroom the following semester.
        \end{itemize}
        }
        \vspace{-1em}
         
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    