
    \medskip

    \myheader{Preprints and Publications}

    \medskip
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.05\textwidth}  p{0.85\textwidth}}
    
2022 & 
        H Bray, R Canary, L-Y Kao, and G Martone. \textit{Counting, equidistribution and entropy gaps at infinity with applications to cusped Hitchin representations}. (2022). 
        \textbf{Journal f\"ur die reine und angewandte Mathematik (Crelles Journal)}.\\ 

2021 & 
        H Bray, R Canary, L-Y Kao, and G Martone. \textit{Pressure metrics for cusped Hitchin components}. (2021). 
         \textbf{Preprint}. \url{https://arxiv.org/abs/2111.07493}\\ 

2021 & 
        H Bray and G Tiozzo. \textit{A global shadow lemma and logarithm law for geometrically finite Hilbert geometries}. (2021). 
         \textbf{Preprint}. \url{https://arxiv.org/abs/2111.04618}\\ 

2021 & 
        H Bray and D Constantine. \textit{Entropy rigidity for finite volume strictly convex projective manifolds}. (2021). 
        \textbf{Geometrie Dedicata}. Vol 214: 543-557.\\ 

2021 & 
        H Bray, R Canary, and L-Y Kao. \textit{Pressure metrics for deformation spaces of quasifuchsian groups with parabolics}. (2021). 
        Accepted at \textbf{Algebraic and Geometric Topology}.\\ 

2021 & 
        H Bray, D Davis, K Lindsey, and C Wu. \textit{The Shape of Thurston's Master Teapot}. (2021). 
        \textbf{Advances in Mathematics}. Vol 377: 107481.\\ 

2020 & 
        H Bray. \textit{Ergodicity of Bowen-Margulis measure for the Benoist 3-manifolds}. (2020). 
        \textbf{Journal of Modern Dynamics}. Vol 16: (0) 305-329.\\ 

2020 & 
        H Bray. \textit{Geodesic flow of nonstrictly convex Hilbert geometries}. (2020). 
        \textbf{Annales de l'Institute Fourier}. Vol 70: (4) 1563-1593.\\ 

2019 & 
        I Adeboye, H Bray, and D Constantine. \textit{Entropy rigidity and Hilbert volume}. (2019). 
        \textbf{Discrete Contin. Dyn. Syst. Ser. A}. Vol 39: (4) 1731-1744.
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    