
    \medskip

    \myheader{Service and Leadership}

    \medskip
    \medskip



    \textbf{\large Leadership}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.2}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
     Sep.  2022 --  Aug.  2023 & \textbf{Director}. \textit{Mason Experimental Geometry Lab (MEGL)}.  \\ 
 Sep.  2020 --  Aug.  2022 & \textbf{Director of Outreach}. \textit{Mason Experimental Geometry Lab (MEGL)}.  \\ 
 Aug.  2020 & \textbf{Assistant to the organizers}. \textit{University of Michigan}.  Inquiry Based Learning Workshop.  \\ 
 Jul.  2017 --  May  2020 & \textbf{Director}. \textit{Lab of Geometry at Michigan (LoGM)}.  \\ 
 Jun.  --  Jul.  2017 & \textbf{Assistant to the organizers}. \textit{Mathematical Research Community Workshop on Dynamical Systems: Smooth, Symbolic, and Measurable}.  \\ 
 Sep.  2014 --  May  2016 & \textbf{President}. \textit{Tufts University Student Chapter of the Association for Women in Math (AWM)}.  \\ 
 Sep.  2013 --  Aug.  2014 & \textbf{Vice-President, Co-founder}. \textit{Tufts University Student Chapter of the Association for Women in Math (AWM)}.  \\ 
 Sep.  2012 --  Aug.  2013 & \textbf{Second Year Class Representative}. \textit{Tufts University Org. of Graduate Students in Mathematics}.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    

    \textbf{\large Organizational Work}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.2}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
      Spring 2022 --    present & \textbf{Co-Organizer}. \textit{George Mason University}.  Geometry Seminar (MMA: metrics, measures, and algorithms).  \\ 
 Jan.  --  Apr.  2020 & \textbf{Co-Organizer}. \textit{University of Michigan}.  Inquiry Based Learning Lunch.  \\ 
16 Jan.  2020 & \textbf{Co-Organizer}. \textit{Joint Mathematics Meetings}.  So you're going to be a postdoc, now what? A Mathematical Association of America (MAA) Panel.  \\ 
10  -- 14 Jun.  2019 & \textbf{Co-Organizer}. \textit{University of Michigan}.  LG\&TBQ: a conference celebrating the work of diverse mathematicians
in geometry, topology, and dynamics.  \\ 
 Sep.  2014 --  Apr.  2016 & \textbf{Organizer}. \textit{Tufts University}.  Dynamics Seminar.  \\ 
 May  2014 & \textbf{Co-Organizer}. \textit{Research in Pairs}.  Joint with Micka\"el Crampon.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    

    \textbf{\large Committee Work}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.2}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
     Jul.  2024 & \textbf{Qualifying Exam Committee Member}. \textit{George Mason University}.  Doctoral candidate Jeanie Schreiber, advised by Tyrus Berry.  \\ 
 May  2022 & \textbf{Hiring Committee Member}. \textit{George Mason University}.  \\ 
 Apr.  2020 & \textbf{Dissertation Committee Member}. \textit{University of Michigan}.  Doctoral candidate Samantha Pinella, advised by Ralf Spatzier.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    

    \textbf{\large Professional Service}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.2}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
    1 Feb.  2023 -- 31 Jan.  2026 & \textbf{Mathematics Research Communities Advisory Board}. \textit{American Mathematical Society}.  \\ 
23 Feb.  2024 & \textbf{SIAM Faculty Symposium Lecturer}. \textit{George Mason Department of Mathematical Sciences}.  \\ 
 Feb.  2023 & \textbf{Math department representative}. \textit{College of Science User Group Interviews}.  \\ 
6 Jan.  2023 & \textbf{Recruiter and GMU Representative}. \textit{Joint Mathematics Meetings Graduate Fair}.  \\ 
  Spring 2023 & \textbf{Mentor}. \textit{George Mason Department of Mathematical Sciences}.  Mentored and trained new faculty member and Mason Experimental Geometry Lab (MEGL) outreach director Rosemberg Toala.  \\ 
21  -- 22 May  2021 & \textbf{Co-Facilitator}. \textit{DC-MD-VA Communities for Mathematics Inquiry in Teaching (COMMIT) Network}.  Workshop on Standards Based Grading and Active Learning.  \\ 
2 Apr.  2021 & \textbf{Co-Facilitator}. \textit{George Mason University}.  Active Learning Discussion Series: on Equity in the Classroom.  \\ 
16 Jan.  2019 & \textbf{Panelist}. \textit{Joint Mathematics Meetings}.  Association for Women in Mathematics Panel: Promoting Inclusion in Stem.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    

    \textbf{\large Community Outreach}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.2}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
    28 May  2024 & \textbf{Mason TV filmed presenter}. \textit{Mason Experimental Geometry Lab (MEGL)}.  \\ 
12 Mar.  2024 & \textbf{Activity Facilitator}. \textit{Lewis Coates Elementary School}.  Mason Experimental Geometry Lab (MEGL) Outreach Event.  \\ 
3 Dec.  2022 & \textbf{Activity Facilitator}. \textit{Mason Early Identification STEM Fusion program}.  Making Mathematics Meaningful.  \\ 
 Sep.  2020 & \textbf{Director of Outreach}. \textit{Mason Experimental Geometry Lab (MEGL)}.  \\ 
8 Mar.  2020, 22 Mar.  2020 & \textbf{Activity Facilitator}. \textit{University of Michigan Math Circle}.  Middle school students.  \\ 
 Oct.  --  Nov.  2017 & \textbf{Activity Facilitator}. \textit{Wolverine Pathways}.  High school students.  \\ 
 Nov.  2016,  Mar.  2017,  Nov.  2017 & \textbf{Activity Facilitator}. \textit{Females Excelling in Math, Engineering, and the Sciences (FEMMES) Capstone Event}.  4th-6th grade girls.  \\ 
 Jul.  2012 & \textbf{Instructor}. \textit{MISE Math Camp}.  Accra, Ghana.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    