
    \medskip

    \myheader{Conferences, Seminars, Workshops, and Visits}

    \medskip
    \medskip



    \textbf{\large Invited Presentations}
    
    \begin{center}
    {
      \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
    6 Jan.  2023 & \textbf{Joint Mathematics Meeting AMS-Spectra Special Session on Research by LGBTQ+ Mathematicians}.  Boston, MA.  \\ 
 Jan.  2023 & \textbf{Joint Mathematics Meeting Special Session: Dynamics, Geometry \& Group Actions}.  Boston, MA.  \\ 
1 Nov.  2022 & \textbf{Geometry Seminar}. \textit{University of Virginia}.  Charlottesville, VA.  \\ 
11 Nov.  2022 & \textbf{Topology, Algebra, and Dynamics Seminar}. \textit{George Mason University}.  Fairfax, VA.  \\ 
1 Nov.  2022 & \textbf{Geometry Seminar}. \textit{University of Virginia}.  Charlottesville, VA.  \\ 
19 Sep.  2022 & \textbf{Geometry Seminar}. \textit{George Mason University}.  Fairfax, VA.  \\ 
14  -- 25 Jun.  2021 & \textbf{The Nearly Carbon Neutral Geometric Topology Conference}. (virtual) \\ 
23 Mar.  2021 & \textbf{Topology and Geometry Seminar}. \textit{Florida State University}.  Tallahassee, FL. (virtual) \\ 
18 Nov.  2020 & \textbf{Max Dehn Seminar}. \textit{University of Utah}.  Salt Lake City, UT. (virtual) \\ 
10 Apr.  2020 & \textbf{Geometry and Topology Seminar}. \textit{Columbia University}.  New York, NY. (virtual) \\ 
18 Nov.  2019 & \textbf{Geometry and Discrete Groups Seminar}. \textit{Institute Hautes \'Etudes Scientifiques (IHES)}.  Bures-sur-Yvette, France.  \\ 
24  -- 28 Jun.  2019 & \textbf{Perspectives on convex projective geometry}.  S\`ete, France.  \\ 
4  -- 6 Jun.  2019 & \textbf{Boundaries of random walks}. \textit{Bowdoin College}.  Brunswick, ME.  \\ 
27  -- 31 May  2019 & \textbf{Dynamics of group actions: a conference in the honor of Yves Benoist}.  Cetraro, Italy.  \\ 
11 Apr.  2019 & \textbf{Geometric Group Theory Seminar}. \textit{Ohio State University}.  Columbus, OH.  \\ 
16  -- 19 Jan.  2019 & \textbf{Joint Mathematics Meeting Special Session on Geometry Labs United: Research, Visualization, and Outreach}.  Baltimore, MD.  \\ 
30 Jul.  -- 3 Aug.  2018 & \textbf{Conference on group actions and ergodic theory in geometry and topology}. \textit{The Hamilton Mathematics Institute}.  Dublin, Ireland.  \\ 
30 Apr.  2018 & \textbf{Dynamics seminar}. \textit{University of Chicago}.  Chicago, IL.  \\ 
10  -- 13 Jan.  2018 & \textbf{Joint Mathematics Meeting Special Session: Boundaries for groups and spaces}.  San Diego, CA.  \\ 
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    
    
