
    \medskip

    \myheader{Conferences, Seminars, Workshops, and Visits}

    \medskip
    \medskip



    \textbf{\large Invited Presentations}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
    18 Jul.  2024 & \textbf{Moving to higher rank: 
from hyperbolic to Anosov.
A conference in honor of Dick Canary}.  Cetraro, Italy.  \\ 
28 Apr.  2024 & \textbf{Knots in Washington 49.9843375}. \textit{George Washington University}.  Washington, DC.  \\ 
10 Apr.  2024 & \textbf{RTG seminar on geometry, topology, and dynamics}. \textit{University of Michigan}.  Ann Arbor, MI.  \\ 
18 Mar.  -- 1 Apr.  2024 & \textbf{Minicourse on logarithm laws for hyperbolic metric spaces}. \textit{George Mason University}.  Fairfax, VA. (3 courses) \\ 
1 Feb.  2024 & \textbf{Randomness and Geometry Seminar}. \textit{Fields Institute}.  Toronto, ON, Canada.  \\ 
2 Dec.  2023 & \textbf{Collaborative team conference}.  Charlottesville, VA.  \\ 
9 Feb.  2023 & \textbf{Dynamics Seminar}. \textit{University of Maryland}.  College Park, MD.  \\ 
6 Jan.  2023 & \textbf{Joint Mathematics Meeting AMS-Spectra Special Session on Research by LGBTQ+ Mathematicians}.  Boston, MA.  \\ 
4 Jan.  2023 & \textbf{Joint Mathematics Meeting Special Session: Dynamics, Geometry \& Group Actions}.  Boston, MA.  \\ 
9 Dec.  2022 & \textbf{Knots in Washington 49.875}. \textit{George Washington University}.  Washington, DC.  \\ 
11 Nov.  2022 & \textbf{Topology, Algebra, and Dynamics Seminar}. \textit{George Mason University}.  Fairfax, VA.  \\ 
1 Nov.  2022 & \textbf{Geometry Seminar}. \textit{University of Virginia}.  Charlottesville, VA.  \\ 
19 Sep.  2022 & \textbf{Geometry Seminar}. \textit{George Mason University}.  Fairfax, VA.  \\ 
14  -- 25 Jun.  2021 & \textbf{The Nearly Carbon Neutral Geometric Topology Conference}. (virtual) \\ 
23 Mar.  2021 & \textbf{Topology and Geometry Seminar}. \textit{Florida State University}.  Tallahassee, FL. (virtual) \\ 
18 Nov.  2020 & \textbf{Max Dehn Seminar}. \textit{University of Utah}.  Salt Lake City, UT. (virtual) \\ 
10 Apr.  2020 & \textbf{Geometry and Topology Seminar}. \textit{Columbia University}.  New York, NY. (virtual) \\ 
18 Nov.  2019 & \textbf{Geometry and Discrete Groups Seminar}. \textit{Institute Hautes \'Etudes Scientifiques (IHES)}.  Bures-sur-Yvette, France.  \\ 
24  -- 28 Jun.  2019 & \textbf{Perspectives on convex projective geometry}.  S\`ete, France.  \\ 
4  -- 6 Jun.  2019 & \textbf{Boundaries of random walks}. \textit{Bowdoin College}.  Brunswick, ME.  \\ 
27  -- 31 May  2019 & \textbf{Dynamics of group actions: a conference in the honor of Yves Benoist}.  Cetraro, Italy.  \\ 
11 Apr.  2019 & \textbf{Geometric Group Theory Seminar}. \textit{Ohio State University}.  Columbus, OH.  \\ 
16  -- 19 Jan.  2019 & \textbf{Joint Mathematics Meeting Special Session on Geometry Labs United: Research, Visualization, and Outreach}.  Baltimore, MD.  \\ 
30 Jul.  -- 3 Aug.  2018 & \textbf{Conference on group actions and ergodic theory in geometry and topology}. \textit{The Hamilton Mathematics Institute}.  Dublin, Ireland.  \\ 
30 Apr.  2018 & \textbf{Dynamics seminar}. \textit{University of Chicago}.  Chicago, IL.  \\ 
10  -- 13 Jan.  2018 & \textbf{Joint Mathematics Meeting Special Session: Boundaries for groups and spaces}.  San Diego, CA.  \\ 
2 May  2017 & \textbf{Dynamical Systems Seminar}. \textit{Northwestern University}.  Evanston, IL.  \\ 
22 Apr.  2017 & \textbf{Junior Geometry and Topology in the Midwest Conference}. \textit{University of Wisconsin}.  Madison, WI.  \\ 
13 Mar.  2017 & \textbf{Geometry and Topology Seminar}. \textit{University of Toronto}.  Toronto, ON, Canada.  \\ 
9 Feb.  2017 & \textbf{Ergodic Theory/Probability Seminar}. \textit{Ohio State University}.  Columbus, OH.  \\ 
28 Nov.  2016 & \textbf{Complex Analysis, Dynamics, and Geometry seminar}. \textit{University of Michigan}.  Ann Arbor, MI.  \\ 
4 Nov.  2016 & \textbf{Howard University Mathematics Colloquium}.  Washington, DC.  \\ 
27  -- 30 Oct.  2016 & \textbf{Workshop in Dynamical Systems}. \textit{Pennsylvania State University}.  State College, PA.  \\ 
2  -- 11 Aug.  2016 & \textbf{Minicourse on ergodic geometry in a nonuniformly hyperbolic setting (3 classes)}. \textit{University of Maryland}.  College Park, MD. (4 courses) \\ 
26 Apr.  2016 & \textbf{Dynamics and Algebra seminar}. \textit{Wesleyan University}.  Middletown, CT.  \\ 
15 Feb.  2016 & \textbf{Dynamics seminar}. \textit{University of Chicago}.  Chicago, IL.  \\ 
3 Dec.  2015 & \textbf{Everytopic seminar}. \textit{Brandeis University}.  Waltham, MA.  \\ 
31 Oct.  2015 & \textbf{Midwest Dynamical Systems Meeting}. \textit{Ohio State University}.  Columbus, OH. (poster) \\ 
21 Feb.  2015 & \textbf{Graduate Student Math Conference}. \textit{Brown University}.  Providence, RI.  \\ 
12 May  2014 & \textbf{IRMA Master Class: student-postdoc seminar}. \textit{University of Strasbourg}.  Strasbourg, France.  \\ 
31 Mar.  2014 & \textbf{School on Geometry and Dynamics}. \textit{Centre International de Rencontres Math\'ematiques (CIRM)}.  Luminy, France. (poster) \\ 
28 Mar.  2014 & \textbf{S\'eminaire Teich}. \textit{Aix-Marseille University}.  Marseille, France.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    

    \textbf{\large Conferences Attended}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
    6  -- 12 Aug.  2023 & \textbf{Collaborative projects in geometric topology}.  Lexington, VA.  \\ 
4  -- 7 Oct.  2018 & \textbf{Workshop in Dynamical Systems and Related Topics}. \textit{Pennsylvania State University}.  State College, PA.  \\ 
12  -- 13 Aug.  2017 & \textbf{Geometry Labs United}. \textit{University of Washington}.  Seattle, WA.  \\ 
18  -- 24 Jun.  2017 & \textbf{Mathematical Research Community Workshop on Dynamical Systems:
Smooth, Symbolic, and Measurable}.  Snowbird Resort, UT.  \\ 
15  -- 19 Aug.  2016 & \textbf{Workshop on Moduli Spaces of Geometric Structures}. \textit{Institute for Mathematical Sciences}.  Singapore.  \\ 
22  -- 24 Jun.  2016 & \textbf{Geometries, surfaces and representations of fundamental groups}. \textit{University of Maryland}.  College Park, MD.  \\ 
15  -- 17 Apr.  2016 & \textbf{Workshop on Dynamical Systems and Related Topics}. \textit{University of Maryland}.  College Park, MD.  \\ 
7  -- 11 Mar.  2016 & \textbf{Fractal Geometry, Hyperbolic Dynamics and Thermodynamical Formalism}. \textit{Institute for Computational and Experimental Research in Mathematics (ICERM)}.  Providence, RI.  \\ 
6  -- 9 Jan.  2016 & \textbf{Joint Mathematics Meetings}.  Seattle, WA.  \\ 
14  -- 15 Nov.  2015 & \textbf{AMS Fall Eastern Sectional Meeting}. \textit{Rutgers University}.  New Brunswick, NJ.  \\ 
19 Sep.  2015 & \textbf{Women In Mathematics In New England (WiMiN)}. \textit{Smith College}.  Northampton, MA.  \\ 
20  -- 23 Jan.  2015 & \textbf{MSRI Introductory Workshop: Dynamics on Moduli Spaces of Geometric Structures}. \textit{Mathematical Sciences Research Institute (MSRI)}.  Berkeley, CA.  \\ 
15  -- 16 Jan.  2015 & \textbf{MSRI Connections for Women: Dynamics on Moduli Spaces of Geometric Structures}. \textit{Mathematical Sciences Research Institute (MSRI)}.  Berkeley, CA.  \\ 
4  -- 14 Jun.  2014 & \textbf{ICTP-NLAGA School in Dynamical Systems and Ergodic Theory}. \textit{African Institute for Mathematical Sciences (AIMS)}.  Dakar, Senegal.  \\ 
9  -- 17 May  2014 & \textbf{IRMA Master Class: Around Thurston-Grothendieck-Teichm\"uller theories}. \textit{University of Strasbourg}.  Strasbourg, France.  \\ 
 Apr.  2014 & \textbf{Finsler Geometry and Applications}. \textit{Galatasaray University}.  Istanbul, Turkey.  \\ 
20  -- 24 Jan.  2014 & \textbf{Young Researchers in Geometric Groupy Theory}. \textit{Centre International de Rencontres Math\'ematiques (CIRM)}.  Luminy, France.  \\ 
2  -- 6 Dec.  2013 & \textbf{Hyperbolicity and Dimension}. \textit{Centre International de Rencontres Math\'ematiques (CIRM)}.  Luminy, France.  \\ 
29 Nov.  2013 & \textbf{Young Mathematicians in Dynamical Systems}. \textit{Centre International de Rencontres Math\'ematiques (CIRM)}.  Luminy, France.  \\ 
27 May  -- 6 Jun.  2013 & \textbf{Beyond Uniform Hyperbolicity}.  B\c{e}dlewo, Poland.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    

    \textbf{\large Seminars Attended}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
    12 Feb.  2024 & \textbf{Topology Seminar}. \textit{University of Maryland}.  College Park, MD.  \\ 
 Jan.  2022 -- present & \textbf{Geometry Seminar (MMA: metrics, measures, and algorithms)}. \textit{George Mason University}.  Fairfax, VA.  \\ 
 Sep.  2016 --  May  2020 & \textbf{RTG working seminar on geometry, topology, and dynamics}. \textit{University of Michigan}.  Ann Arbor, MI.  \\ 
 Sep.  2016 --  May  2020 & \textbf{Topology seminar}. \textit{University of Michigan}.  Ann Arbor, MI.  \\ 
 Sep.  2014 --  May  2016 & \textbf{Geometric Group Theory and Topology Seminar}. \textit{Tufts University}.  Medford, MA.  \\ 
 Feb.  --  Apr.  2014 & \textbf{S\'eminaire: Dynamique, Arithm\'ethique et Combinatoire}. \textit{Institut de Math\'ematiques de Marseille}.  Marseille, France.  \\ 
 Jan.  --  Apr.  2014 & \textbf{S\'eminaire: Teich}. \textit{Aix-Marseille University}.  Marseille, France.  \\ 
 Sep.  2012 --  Dec.  2013 & \textbf{Dynamics Seminar}. \textit{Tufts University}.  Medford, MA.  \\ 
  Spring 2013 & \textbf{Working seminar on Ergodic Geometry}. \textit{Tufts University}.  Medford, MA.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    

    \textbf{\large Invited Visits}
    
    \begin{center}
    {
    \renewcommand{\arraystretch}{1.5}
    \begin{longtable}{p{0.2\textwidth}  p{0.7\textwidth}}
    22 Jan.  -- 2 Feb.  2024 & \textbf{Randomness and Geometry Thematic Semester}. \textit{Fields Institute}.  Toronto, ON, Canada.  \\ 
8  -- 12 Aug.  2022 & \textbf{Invited Guest}. \textit{University of Wisconsin}.  Madison, WI.  \\ 
 Nov.  2019 & \textbf{Invited Guest}. \textit{Institute Hautes \'Etudes Scientifiques (IHES)}.  Bures-sur-Yvette, France.  \\ 
 Jan.  --  Apr.  2014 & \textbf{Invited Guest}. \textit{Centre International de Rencontres Math\'ematiques (CIRM)}.  Luminy, France.  
    \end{longtable}
    } 
    \end{center}

    \vspace{-1em}
    